### 2017-08-19 paper/incomeShocks-jde-r1.tex
Add Logit results to Appendix

% Logit versions of main dummy set-up

\begin{table}[htbp]
\begin{center}
\begin{small}
\begin{threeparttable}
\caption{The Effects of Crop Loss -- Logit Fixed Effects Estimates}
\label{tab:logit}
\begin{tabular}{@{} l D{.}{.}{2.6} D{.}{.}{2.6}  D{.}{.}{2.6} D{.}{.}{2.6} D{.}{.}{2.6}  @{}}
\toprule
                                                       & \mco{}              &\mco{}               &\multicolumn{3}{c}{Contraceptive Use}\\ \cmidrule(lr){4-6}
                                                       & \mco{Pregnant}      &\mco{Birth}          &\mco{Any}            &\mco{Traditional}    & \mco{Modern}        \\ \midrule
 & \multicolumn{5}{l}{Without interaction with assets} \\
Crop loss - 1-7 months                                 &      -0.607\sym{**} &                     &       0.804\sym{**} &       0.764\sym{*}  &       0.299         \\
                                                       &     (0.274)         &                     &     (0.390)         &     (0.444)         &     (0.691)         \\
Crop loss - 7-14 months                                &                     &      -0.946\sym{***}&                     &                     &                     \\
                                                       &                     &     (0.294)         &                     &                     &                     \\
\addlinespace 
 & \multicolumn{5}{l}{With interaction with assets} \\
Crop loss - 1-7 months                                 &      -0.570\sym{*}  &                     &       1.107\sym{**} &       0.934\sym{*}  &       1.379         \\
                                                       &     (0.335)         &                     &     (0.449)         &     (0.500)         &     (0.945)         \\
Crop loss - 1-7 months                                 &      -0.006         &                     &      -0.027         &      -0.013         &      -0.070         \\
\hs \X initial assets (10,000 TZS)                                                       &     (0.032)         &                     &     (0.021)         &     (0.019)         &     (0.045)         \\
Crop loss - 7-14 months                                &                     &      -0.952\sym{***}&                     &                     &                     \\
                                                       &                     &     (0.337)         &                     &                     &                     \\
Crop loss - 7-14 months                                &                     &       0.001         &                     &                     &                     \\
\hs \X initial assets (10,000 TZS)                     &                     &     (0.020)         &                     &                     &                     \\
\addlinespace 
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Woman fixed effects                                    &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Observations                                           &    \mco{560}        &    \mco{360}        &    \mco{300}        &    \mco{228}        &     \mco{88}        \\
Number of women                                        &    \mco{140}        &    \mco{120}        &     \mco{75}        &     \mco{57}        &     \mco{22}        \\
\bottomrule
\end{tabular}
\begin{tablenotes} \footnotesize
\item \hspace*{-0.5em} \textbf{Note.}
Robust standard errors clustered at household level in parentheses; 
* significant at 10\%; ** significant at 5\%; *** significant at 1\%.
Crop loss is a dummy for a per capita crop loss of 200 TZS or above.
Assets are per capita and measured in 10,000 TZS.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{center}
\end{table}

>>>>

% Logit versions of main dummy set-up
\input{../tables/appendix_logit.tex}
